---
title: "DSC 200 - 202 Course Project"
date: "6 March 2021"
output: pdf_document
---


Group Number:

Group Members' Names (IDs):

1. Abc Xyz (00000000)   -- Team Leader
2.                      -- Member 1
3.                      -- Member 2
4.                      -- Member 3



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Loading Libraries    

*Note: The team leader and members should run the code below.*

```{r libraries, echo=FALSE, message = FALSE}
library(tidyverse)
library(readxl)
```


*Note: Only Team Leader should run the code below*

```{r load_data, message = FALSE}
tdata <- read_excel("teachers_data.xlsx")
```


## Task 1 - Tidy Data
\textcolor{red}{(8 points)}

```{r tidy_data}
#Add some code
```

Team Leader should *Knit, commit, and push changes to GitHub with an appropriate commit message. Make sure to commit and push all changed files so that your Git pane is cleared up afterwards.*


## Task2 - Analysis
\textcolor{red}{(8 points)}

Next Team Member should *Pull the changes made by Team Leader before proceeding.*

(a) What are the different administrative_regions (المنطقة الإدارية) found in the data?

```{r admin_regions}
#Add some code
```

Comments about your answer:

(b) Based on your knowledge of the administrative regions in Saudi Arabia, is there any region that has not recruited any teacher during the period under review (1437 - 1440 Hijri)? List the Saudi regions shown in the data.

```{r not_recruited_admin_regions}
#Add some code
```

Comments about your answer:

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

## Task3 - Further Analysis and Plots
\textcolor{red}{(20 points)}

The Next Team Member should *Pull the changes made by Member 1 before proceeding.*

(a) Saudi Arabian education is divided into different stages/levels (المرحلة), list the different levels showed in the data in descending order of frequency. (4 points)

```{r study_levels}
#Add some code
```

Comments about your answer:

(b) Which level recruit the most teachers? (4 points)


```{r most_teachers}
#Add some code
```

Comments about your answer:

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

The Next Team member should *Pull the changes made by Team Leader before proceeding.*

(c) Plot the graph of region versus number of **Saudi** teachers recruited over the period. (4 points)

```{r plot_admin_regions_saudi}
#Add some code
```

Comments about your answer:

(d) Plot the graph of region versus number of **Non-Saudi** teachers recruited over the period. (4 points)

```{r plot_admin_regions_non-saudi}
#Add some code
```

Comments about your answer:

(e) Plot the graph of region versus number of **all teachers** recruited over the period. (4 points)

```{r plot_admin_regions_all}
#Add some code
```

Comments about your answer:

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

## Task 4 - Further Analysis and Correlations
\textcolor{red}{(12 points)}

The Next Team member should *Pull the changes made previously before proceeding.*

(a) How many boys and how many girls schools are listed in the data? (4 points)

```{r no_boys_girls}
#Add some code
```

Comments about your answer:

(b) Between boys and girls schools, which recruit more teachers? (4 points)

```{r recruitment_boys_girls}
#Add some code
```

Comments about your answer:

(c) What is the correlation between recruitment at boys schools and recruitment of girls schools? (4 points)

```{r plot_correlation_boys_girls}
#Add some code
```

Comments about your answer:

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

## Task 5 - Final Analysis and Plots
\textcolor{red}{(12 points)}

The Next Team member should *Pull the changes made previously before proceeding.*

(a) How many teachers are recruited each year, 1437, 1438, 1439, and 1440? 

```{r teachers_per_year}
#Add some code
```

Comments about your answer:

(b) Which region recruited the most teachers in each of the years under review? (4 points)

```{r teachers_per_region}
#Add some code
```

Comments about your answer:

(c) Plot the graph of number of teachers recruited vs the number of schools in an administrative region? What type or relationship exist between the two variables? (4 points)

```{r plot_teachers_administrative_regions}
#Add some code
```

Comments about your answer:

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

## If you are here, then congratulations!! You have completed the DSC 200 course project.