---
title: "Analysis of Teachers' Recruitment in Saudi Arabia Between 1437 and 1440"
subtitle: "Data from Saudi Open Data Office"
author: "Musab Isah"
date: "6 March 2021"
output: github_document
---

Group Number:5

Group Members' Names (IDs):

1. Fawzaih Nazal(2201000429) -- Team Leader
2.Manar Mansour(2201002883)    -- Member 1
3.Hajar Eid(2201002337)    -- Member 2
4.Fadiyah suliman(2201001182)  ,wallaa Ali(2201002583) -- Member 3


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Libraries 

Ensure you have the `tidyverse` and `readxl` packages installed by running the 2 lines of code below. Both the team leader and members should run the code below in the console of rstudio.

```{r libraries, echo=FALSE, message = FALSE}
library(tidyverse)
library(readxl)
```


We then need to load the data from the MS Excel (.xlsx) file, named teachers_data.xlsx, to the R environment for processing.

*Note: Only Team Leader should run the code below*

```{r load_data, message = FALSE}
tdata <- read_excel("teachers_data.xlsx")
```

# Wherever you see the text '#Add some code', it means you should delete the comment and add your code for the task.

# 2 Marks will be deducted for every deadline missed.

## Task 1
\textcolor{red}{(8 points)}

```{r tidy_data}
tdata = rename(tdata, administrative_regions = "المنطقة الإدارية")
tdata = rename(tdata, school_Level = "المرحلة")
tdata = rename(tdata, authority = "السلطة")
tdata = rename(tdata, Office_of_Education = "مكتب التربية")
tdata = rename(tdata, sex = "الجنس")
tdata = rename(tdata, School_type = "نوع المدرسة")
tdata = rename(tdata, Type_of_education = "نوع التعليم")
tdata = rename(tdata, school_system = "نظام الدراسة")
tdata = rename(tdata, Saudi_teacher = "معلم سعودي")
tdata = rename(tdata, Non_Saudi_teacher = "معلم غير سعودي")
tdata = rename(tdata, Teachers = "معلمين جملة")
tdata = rename(tdata, the_year = "السنة")
```

Team Leader should *Knit, commit, and push changes to GitHub with an appropriate commit message. Make sure to commit and push all changed files so that your Git pane is cleared up afterwards.*

\textcolor{red}{DEADLINE: END OF WEEK 9}

## Task2
\textcolor{red}{(8 points)}

Next Team Member should *Pull the changes made by Team Leader before proceeding.*

(a) What are the different administrative_regions (Al-Mandaqah Al-idariyyah) found in the data?

```{r admin_regions}
tdata %>% count(administrative_regions) %>% arrange(desc(n))
```

Comments about your answer:the biggest regions ->{riyadh: 31617 ,
makkah : 26944 }

and the smallest-> {alhudood alshmalya : 2072 , najran : 2933}.

(b) Based on your knowledge of the administrative regions in Saudi Arabia, is there any region that has not recruited any teacher during the period under review (1437 - 1440 Hijri)? List the Saudi regions shown in the data.

```{r not_recruited_admin_regions}
tdata %>% filter(the_year>=1437 ,the_year<=1440, Teachers==0)%>% count(administrative_regions)

tdata %>% filter(the_year>=1437 ,the_year<=1440, Saudi_teacher==0)%>% count(administrative_regions)%>%arrange(desc(n))

tdata %>% filter(the_year>=1437 ,the_year<=1440, Non_Saudi_teacher==0)%>% count(administrative_regions)%>%arrange(desc(n))

```

Comments about your answer:The year (1437 to 1440), one non-Saudi  and Saudis teacher was appointed by the administrative regions and most regions, at least one teacher was appointed in Riyadh.

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

\textcolor{red}{DEADLINE: END OF WEEK 10}

## Task3
\textcolor{red}{(20 points)}

The Next Team Member should *Pull the changes made by Member 1 before proceeding.*

(a) Saudi Arabian education is divided into different stages/levels (Al-Marhala), list the different levels showed in the data in descDEADLINE: ENDing order of frequency. (4 points)

```{r study_levels}
count (tdata, "school_Level")
tdata%>%arrange (desc(school_Level))
```

Comments about your answer:that we have 140438 (int)(n) of 
school_level.

(b) Which level recruit the most teachers? (4 points)


```{r most_teachers}
tdata%>%count (school_Level)%>%arrange (desc(n))
```

Comments about your answer:The largest level in recrufitment is the primary schools and the lowest level is the continue learning, so we we should educate and qualify specialized teachers at the primary stage because it is the most important stage in terms of employment requirements and also the most important In students' lives

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

The Next Team member should *Pull the changes made by Team Leader before proceeding.*

(c) Plot the graph of region versus number of **Saudi** teachers recruited over the period. (4 points)

```{r plot_admin_regions_saudi}
ggplot (data=tdata, aes (x=administrative_regions, y= Saudi_teacher)) + geom_point (stat="identity")
```

Comments about your answer: The most number of  Saudi teachers has been employed  in (riyadh) and The fewest number of Saudi teachers have been employed in northern borders

(d) Plot the graph of region versus number of **Non-Saudi** teachers recruited over the period. (4 points)

```{r plot_admin_regions_non-saudi}
ggplot (data=tdata, aes (x=administrative_regions, y= Non_Saudi_teacher)) + geom_point (stat="identity")
```

Comments about your answer: The most number of non Saudi teachers has been employed in ( riyadا ) and The fewest number of saudi teachers have been employed in Albahaa

(e) Plot the graph of region versus number of **all teachers** recruited over the period. (4 points)

```{r plot_admin_regions_all}
ggplot (data=tdata, aes (x=administrative_regions, y= Teachers)) + geom_point (stat="identity")
```

Comments about your answer: The most number of non or Saudi teachers has been employed in (riyad) and The fewest number of saudi teachers have been employed in northern borders

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

\textcolor{red}{DEADLINE: END OF WEEK 12}

## Task 4
\textcolor{red}{(12 points)}

The Next Team member should *Pull the changes made previously before proceeding.*

(a) How many boys and how many girls schools are listed in the data? (4 points)

```{r no_boys_girls}
tdata%>%count(sex)
```

Comments about your answer:
the number of girls schools >> (77462) 
is more then the number of boys schools >> (62766)

(b) Between boys and girls schools, which recruit more teachers? (4 points)

```{r recruitment_boys_girls}
tdata%>%group_by(sex)%>%summarise_at(vars(Teachers),list(sum=sum))
```

Comments about your answer:
boys_schools_teachers = (954028)
girls_schools_teachers = (1166895)
more teachers are employed in girls ’schools than boys’ schools

(c) What is the correlation between recruitment at boys schools and recruitment of girls schools? (4 points)

```{r plot_correlation_boys_girls}
#Add some code
```

Comments about your answer:

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

\textcolor{red}{DEADLINE: END OF WEEK 13}

## Task 5
\textcolor{red}{(12 points)}

The Next Team member should *Pull the changes made previously before proceeding.*

(a) How many teachers are recruited each year, 1437, 1438, 1439, and 1440? 

```{r teachers_per_year}
#Add some code
```

Comments about your answer:

(b) Which region recruited the most teachers in each of the years under review? (4 points)

```{r teachers_per_region}
#Add some code
```

Comments about your answer:

(c) Plot the graph of number of teachers recruited vs the number of schools in an administrative region? What type or relationship exist between the two variables? (4 points)

```{r plot_teachers_administrative_regions}
ggplot(data=tdata, aes(x=sex, y= Teachers , color = sex)) +                              geom_bar(stat="identity")
```

Comments about your answer:
the number of female teachers working in girls ’schools exceeds the number of teachers working in boys’ schools. 
therefore, emphasis must be placed on training and educating female teachers at higher rates to prepare them to work in girls ’schools, and employing more teachers working in boys’ schools

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

\textcolor{red}{DEADLINE: END OF WEEK 14}

## If you are here, then congratulations!! You have completed the DSC 200 course project.
