---
title: "Analysis of Teachers' Recruitment in Saudi Arabia Between 1437 and 1440"
subtitle: "Data from Saudi Open Data Office"
author: "Musab Isah"
date: "6 March 2021"
output: github_document
---

Group Number:5

Group Members' Names (IDs):

1. Fawzaih Nazal(2201000429) -- Team Leader
2.Manar Mansour(2201002883)    -- Member 1
3.Hajar Eid(2201002337)    -- Member 2
4.Fadiyah suliman(2201001182)  ,wallaa Ali(2201002583) -- Member 3


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Libraries 

Ensure you have the `tidyverse` and `readxl` packages installed by running the 2 lines of code below. Both the team leader and members should run the code below in the console of rstudio.

```{r libraries, echo=FALSE, message = FALSE}
library(tidyverse)
library(readxl)
```


We then need to load the data from the MS Excel (.xlsx) file, named teachers_data.xlsx, to the R environment for processing.

*Note: Only Team Leader should run the code below*

```{r load_data, message = FALSE}
tdata <- read_excel("teachers_data.xlsx")
```

# Wherever you see the text '#Add some code', it means you should delete the comment and add your code for the task.

# 2 Marks will be deducted for every deadline missed.

## Task 1
\textcolor{red}{(8 points)}

```{r tidy_data}
tdata = rename(tdata, administrative_regions = "المنطقة الإدارية")
tdata = rename(tdata, school_Level = "المرحلة")
tdata = rename(tdata, authority = "السلطة")
tdata = rename(tdata, Office_of_Education = "مكتب التربية")
tdata = rename(tdata, sex = "الجنس")
tdata = rename(tdata, School_type = "نوع المدرسة")
tdata = rename(tdata, Type_of_education = "نوع التعليم")
tdata = rename(tdata, school_system = "نظام الدراسة")
tdata = rename(tdata, Saudi_teacher = "معلم سعودي")
tdata = rename(tdata, Non_Saudi_teacher = "معلم غير سعودي")
tdata = rename(tdata, Teachers = "معلمين جملة")
tdata = rename(tdata, the_year = "السنة")
```

Team Leader should *Knit, commit, and push changes to GitHub with an appropriate commit message. Make sure to commit and push all changed files so that your Git pane is cleared up afterwards.*

\textcolor{red}{DEADLINE: END OF WEEK 9}

## Task2
\textcolor{red}{(8 points)}

Next Team Member should *Pull the changes made by Team Leader before proceeding.*

(a) What are the different administrative_regions (Al-Mandaqah Al-idariyyah) found in the data?

```{r admin_regions}
tdata %>% count(administrative_regions) %>% arrange(desc(n))
```

Comments about your answer:the biggest regions ->{riyadh: 31617 ,
makkah : 26944 }

and the smallest-> {alhudood alshmalya : 2072 , najran : 2933}.

(b) Based on your knowledge of the administrative regions in Saudi Arabia, is there any region that has not recruited any teacher during the period under review (1437 - 1440 Hijri)? List the Saudi regions shown in the data.

```{r not_recruited_admin_regions}
tdata %>% filter(the_year>=1437 ,the_year<=1440, Teachers==0)%>% count(administrative_regions)

tdata %>% filter(the_year>=1437 ,the_year<=1440, Saudi_teacher==0)%>% count(administrative_regions)%>%arrange(desc(n))

tdata %>% filter(the_year>=1437 ,the_year<=1440, Non_Saudi_teacher==0)%>% count(administrative_regions)%>%arrange(desc(n))

```

Comments about your answer:The year (1437 to 1440), one non-Saudi  and Saudis teacher was appointed by the administrative regions and most regions, at least one teacher was appointed in Riyadh.

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

\textcolor{red}{DEADLINE: END OF WEEK 10}

## Task3
\textcolor{red}{(20 points)}

The Next Team Member should *Pull the changes made by Member 1 before proceeding.*

(a) Saudi Arabian education is divided into different stages/levels (Al-Marhala), list the different levels showed in the data in descDEADLINE: ENDing order of frequency. (4 points)

```{r study_levels}
#Add some code
```

Comments about your answer:

(b) Which level recruit the most teachers? (4 points)


```{r most_teachers}
#Add some code
```

Comments about your answer:

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

The Next Team member should *Pull the changes made by Team Leader before proceeding.*

(c) Plot the graph of region versus number of **Saudi** teachers recruited over the period. (4 points)

```{r plot_admin_regions_saudi}
#Add some code
```

Comments about your answer:

(d) Plot the graph of region versus number of **Non-Saudi** teachers recruited over the period. (4 points)

```{r plot_admin_regions_non-saudi}
#Add some code
```

Comments about your answer:

(e) Plot the graph of region versus number of **all teachers** recruited over the period. (4 points)

```{r plot_admin_regions_all}
#Add some code
```

Comments about your answer:

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

\textcolor{red}{DEADLINE: END OF WEEK 12}

## Task 4
\textcolor{red}{(12 points)}

The Next Team member should *Pull the changes made previously before proceeding.*

(a) How many boys and how many girls schools are listed in the data? (4 points)

```{r no_boys_girls}
#Add some code
```

Comments about your answer:

(b) Between boys and girls schools, which recruit more teachers? (4 points)

```{r recruitment_boys_girls}
#Add some code
```

Comments about your answer:

(c) What is the correlation between recruitment at boys schools and recruitment of girls schools? (4 points)

```{r plot_correlation_boys_girls}
#Add some code
```

Comments about your answer:

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

\textcolor{red}{DEADLINE: END OF WEEK 13}

## Task 5
\textcolor{red}{(12 points)}

The Next Team member should *Pull the changes made previously before proceeding.*

(a) How many teachers are recruited each year, 1437, 1438, 1439, and 1440? 

```{r teachers_per_year}
#Add some code
```

Comments about your answer:

(b) Which region recruited the most teachers in each of the years under review? (4 points)

```{r teachers_per_region}
#Add some code
```

Comments about your answer:

(c) Plot the graph of number of teachers recruited vs the number of schools in an administrative region? What type or relationship exist between the two variables? (4 points)

```{r plot_teachers_administrative_regions}
#Add some code
```

Comments about your answer:

The Team Member should *Knit, commit, and push changes to GitHub with an appropriate commit message.*

\textcolor{red}{DEADLINE: END OF WEEK 14}

## If you are here, then congratulations!! You have completed the DSC 200 course project.
